04_DESeq_sexes

### 2019-10-18 analysis/04_DESeq2_sexes.Rmd
working on  plots of genes with top pca loadings

>>>>

```{r topPCAloadings}
# COX1, COX3, CHGA, PRL, ATP2B4, LOC107055658
topPCAloadings <- c("NP_006917.1", "NP_006921.2","XP_421330.1", "NP_990797.2", "XP_015154447.1", "XP_015156300.1")

plotWGCNAcandidates(vsd.hyp, topPCAloadings, colDataHyp, "Hypothalamus")
plotWGCNAcandidates(vsd.pit, topPCAloadings, colDataPit, "Pituitary")
plotWGCNAcandidates(vsd.gon, topPCAloadings, colDataGon, "Gonads")
